Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-23 paper.tex
Add XFOIL parameters; resolves #18

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, implemented as part of the
open source turbine design software QBlade. Simulations were run with the
default settings and zero Mach number, for the approximate average blade chord
Reynolds numbers encountered in the experiments.

>>>>

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, implemented as part of the
open source turbine design software QBlade. Simulations were run for an angle of
attack range of 0--40 degrees, in increments of 0.5 degrees. Solver parameters
used a 100 panels, a fixed speed, zero Mach number, \texttt{NCrit=9} (default
$\mathrm{e}^n$ transition criteria parameter for an average wind tunnel), and no
forced boundary layer transition. Characteristics for computed for the
approximate average blade chord Reynolds numbers encountered in the tow tank
experiments.
